---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mwivhet: Inference with Many Weak Instruments and Heterogeneity

<!-- badges: start -->

[![R-CMD-check](https://github.com/minhnngo/mwivhet/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/minhnngo/mwivhet/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

Inference in a linear instrumental variable regression model with many potentially weak instruments, in the presence of heterogeneous treatment effects. The package implements procedures from [Yap (2025)](https://www.arxiv.org/abs/2408.11193).

Please refer to the [website](https://minhnngo.github.io/mwivhet) for comprehensive details and a demonstration of the package functions.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
if (!requireNamespace("remotes")) {
  install.packages("remotes")
}
remotes::install_github("minhnngo/mwivhet")
```

## Citation
If you use mwivhet, please cite: https://doi.org/10.48550/arXiv.2408.11193  

## Simulation Demo

### Judge Example without Covariates
```{r}
library(mwivhet)
# Demo for judge example without covariates

# Numerator
LMnum <- GetLM_nocov(df = dnc, X = X, e = e, groupZ = group)

# L3O Variance
LMVar <- L3Ovar_gloop_nocov(df = dnc, group = group, X = X, e = e, MX = MX, Me = Me)

# t-statistic for LM test (compare with std normal)
LMt <- LMnum / sqrt(LMVar)

# Confidence Intervals
# Get coefficients first, then values
CI_coefs <- GetCIcoef_nocov(df = dnc, groupZ = group, X = X, Y = Y, MX = MX, MY = MY)
CI <- GetCIvals(CI_coefs)

print(paste("LM Statistic:", LMt))
print("Confidence Interval:")
print(CI)
```

### Quarter-of-Birth Example with Covariates (1)

```{r}
# Demo for QOB example with covariates

# Numerator
# group indexes every QOB and groupW combination
LMnum <- GetLM(df = dc, X = X, e = e, groupW = groupW, group = group)

# Variance
LMVar <- L3Ovar_gloop_cov(df = dc, group = group, groupW = groupW, X = X, e = e, 
                          MX = MX, Me = Me)

# t-statistic for LM test
LMt <- LMnum / sqrt(LMVar)

# Confidence Intervals (Fast method)
CI_coefs <- GetL3OCIcoef_fast(df = dc, groupW = groupW, group = group, X = X, 
                              Y = Y, MX = MX, MY = MY)
CI <- GetCIvals(CI_coefs)

print(paste("LM Statistic:", LMt))
print("Confidence Interval:")
print(CI)
```

### Quarter-of-Birth Example with Covariates (2)


```{r}
# Demo for QOB example with covariates, using stored G and P. Slower but allows continuous W, Z
# Would give the same results as previous example

# Construct G and P using the package function
GP <- GetGP(group = dc$group, groupW = dc$groupW, n = nrow(dc))

# Numerator
# Note: as.numeric ensures it returns a scalar, not a 1x1 matrix
LMnum <- as.numeric(t(dc$e) %*% GP$G %*% dc$X)

# L3O Variance
LMVar <- L3Ovar_iloop_cov(X = dc$X, e = dc$e, P = GP$P, G = GP$G)

# t-statistic
LMt <- LMnum / sqrt(LMVar)

# Confidence Intervals
CI_coefs <- GetCIcoef_iloop(df = dc, P = GP$P, G = GP$G, X = X, Y = Y, MX = MX, 
                            MY = MY, Z = GP$Z, W = GP$W, noisy = FALSE)
CI <- GetCIvals(CI_coefs)

print(paste("LM Statistic:", LMt))
print("Confidence Interval:")
print(CI)
```
