---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mwivhet: Inference with Many Weak Instruments and Heterogeneity

<!-- badges: start -->

[![R-CMD-check](https://github.com/minhnngo/mwivhet/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/minhnngo/mwivhet/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

Inference in a linear instrumental variable regression model with many potentially weak instruments, in the presence of heterogeneous treatment effects. The package implements procedures from [Yap (2025)](https://www.arxiv.org/abs/2408.11193).

The example below uses the bundled Suffolk County prosecution data. For additional documentation, please refer to the [package website](https://minhnngo.github.io/mwivhet). 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
if (!requireNamespace("remotes")) {
  install.packages("remotes")
}
remotes::install_github("minhnngo/mwivhet")
```

## Citation
If you use mwivhet, please cite: https://doi.org/10.48550/arXiv.2408.11193  

## Suffolk County Application

### The following code shows the application of the method in investigating the effect of misdemeanor prosecution (X) on criminal complaint in two years (Y), based on the paper Misdemeanor Prosecution [(Agan et al., 2023)](https://doi.org/10.1093/qje/qjad005).

```{r, message = FALSE, warning = FALSE}
library(mwivhet)
library(dplyr)
library(fixest)

# 0. Setup ----------------------------------------------------------------
df <- suffolk

# 1. Preparation ----------------------------------------------------------
# 1.1. Variable Assignment
df <- df %>%
  mutate(
    X = ng_immed_all,
    Y = anyr_twoyears_arrest2,
    groupZ = first_pros
  )

# 1.2. Construct Covariate Groups (groupW)
df <- df %>%
  mutate(
    monthID = as.integer(factor(court_month2)),
    dowID   = as.integer(factor(court_dow2)),
    groupW  = as.integer(factor(paste(dowID, monthID, sep = "_")))
  )

# 1.3. Construct Interaction Groups (groupQ / group)
df <- df %>%
  mutate(
    groupQ = as.integer(factor(paste(groupW, groupZ, sep = "_"))),
    group  = groupQ
  )

# 1.4. Filter for Group Size
df <- df %>%
  group_by(groupQ) %>%
  filter(n() >= 4) %>%
  ungroup()


# 1.5. Get residualized objects
lmX <- fixest::feols(X~1|group,data=df)
df$MX <- lmX$residuals

lmY <- fixest::feols(Y~1|group,data=df)
df$MY <- lmY$residuals

# 2. Inference ------------------------------------------------------------
S_hat <- GetLM(df, X, X, groupW, group, noisy = FALSE)
JIVE <- GetLM(df, X, Y, groupW, group, noisy = FALSE)/S_hat 

L3OCIcoef <- GetCIcoef(df, groupW, group, X, Y, MX, MY, noisy = FALSE)
L3OCI <- GetCItypebd(L3OCIcoef)[2:3] 

# 3. Table ----------------------------------------------------------------
# 3.1. Create the matrix using calculated L3O variables
L3O_data <- matrix(c(
  L3OCI[1],                # Lower Bound
  L3OCI[2],                # Upper Bound
  JIVE,                    # Point Estimate
  L3OCI[2] - L3OCI[1]      # CI Length
), ncol = 1)

# 3.2. Add labels for row/col
rownames(L3O_data) <- c("LB", "UB", "Estimate", "CIlength")
colnames(L3O_data) <- "L3O"

# 3.3 Round and save
CItab_L3O_round <- round(L3O_data, 3)
CItab_L3O_round
```

